Usage metrics

### 2020-12-09 inst/analysis/usage_metrics.Rmd

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
  calls_packages_path: /run/package-evals-traced.9/summarized-packages.fst
  corpus_path: /revalstudy/inst/data/corpus.fst
---

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: /var/lib/R/project-evalR
  calls_packages_path: /run/package-evals-traced.9/summarized-packages.fst
  corpus_path: /run/package-evals-traced.9/corpus.fst
---
